A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-03-01 sections/Appendix.tex
S4 and Appendix lemma sync (minor swap of letters)

\subsection{False Lemmas in DK's papers}
\label{appendix:false_lemmas}

@@

Let's first recall the lemma:
\begin{lemma}[Subsumption]
Given $\Psi' \le \Psi$:
\begin{enumerate}
    \item If $\Psi \vdash e \Lto A$ and $\Psi \vdash A \le A'$ then $\Psi' \vdash e \Lto A$;
    \item If $\Psi \vdash e \To B$ then there exists
        $A'$ s.t. $\Psi \vdash B' \le B$ and $\Psi' \vdash e \To B$;
    \item If $\Psi \vdash \appInf{C}{e}{A}$ and $\Psi \vdash C' \le C$,
        then there exists $A'$ s.t. $\Psi \vdash A' \le A$ and $\Psi' \vdash \appInf{C'}{e}{A'}$.
\end{enumerate}
\end{lemma}

@@

The proof is by a nested mutual induction on the lexicographical order of the measures
$$\langle |e|_e, |\cdot|_\Leftrightarrow, |A \to B|_\forall \rangle,$$
where the second measure is 2 for checking (1), 1 for inference (2) and 3 for application inference (3);
and the third measure does not apply to case (2) since no $A$ is used.

All but two cases can be finished easily following the declarative typing derivation,
and the proof shares a similar structure to DK's.
One tricky case related to Rule $\mathtt{Decl\forall I}$ inducates that $A$ has the shape $\all A_0$,
thus the subtyping relation derives from either $\mathtt{{\le}\forall L}$ or $\mathtt{{\le}\forall R}$.
For each of the case, the third measure $|A \to B|_\forall$ decreases
(the $\mathtt{{\le}\forall L}$ case requires a type substitution lemma obtaining
$\Psi \vdash e \Lto [\tau/a]A_0$ from the typing derivation).

Another tricky case is $\mathtt{Decl{\to}I}$.
When the subtyping relation is derived from $\mathtt{{\le}{\to}}$,
a simple application of induction hypothesis finishes the proof.
When the subtyping relation is derived from $\mathtt{{\le}\forall R}$,
$|B|_\forall$ decreases, and thus the induction hypothesis finishes this case.

>>>>

\subsection{Broken Lemmas in DK's papers}
\label{appendix:false_lemmas}

@@

Let's first recall the lemma:
\begin{lemma}[Subsumption]
Given $\Psi' \le \Psi$:
\begin{enumerate}
    \item If $\Psi \vdash e \Lto A$ and $\Psi \vdash A \le A'$ then $\Psi' \vdash e \Lto A'$;
    \item If $\Psi \vdash e \To B$ then there exists
        $B'$ s.t. $\Psi \vdash B' \le B$ and $\Psi' \vdash e \To B'$;
    \item If $\Psi \vdash \appInf{A}{e}{C}$ and $\Psi \vdash A' \le A$,
        then there exists $C'$ s.t. $\Psi \vdash C' \le C$ and $\Psi' \vdash \appInf{A'}{e}{C'}$.
\end{enumerate}
\end{lemma}

@@

The proof is by a nested mutual induction on the lexicographical order of the measures
$$\langle |e|_e, |\cdot|_\Leftrightarrow, |A|_\forall + |A'|_\forall \rangle,$$
where the second measure is 2 for checking (1), 1 for inference (2) and 3 for application inference (3);
and the third measure does not apply to case (2) since no $A$ is used.

All but two cases can be finished easily following the declarative typing derivation,
and the proof shares a similar structure to DK's.
One tricky case related to Rule $\mathtt{Decl\forall I}$ inducates that $A$ has the shape $\all A_0$,
thus the subtyping relation derives from either $\mathtt{{\le}\forall L}$ or $\mathtt{{\le}\forall R}$.
For each of the case, the third measure $|A|_\forall + |A'|_\forall$ decreases
(the $\mathtt{{\le}\forall L}$ case requires a type substitution lemma obtaining
$\Psi \vdash e \Lto [\tau/a]A_0$ from the typing derivation).

Another tricky case is $\mathtt{Decl{\to}I}$.
When the subtyping relation is derived from $\mathtt{{\le}{\to}}$,
a simple application of induction hypothesis finishes the proof.
When the subtyping relation is derived from $\mathtt{{\le}\forall R}$,
$|A'|_\forall$ decreases, and thus the induction hypothesis finishes this case.
